---
title: "ZGlab10"
date: "October 17, 2018"
output: 
  html_document:
    toc: yes
    toc_float: yes
    highlights: pygments
    theme: spacelab
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Q1
```{r q1}
source('./Lab10.R')
source('./newtraph.R')
library(purrr)
getwd()
```

##Q2
Line A of mymaxlik gets the cartesian product of the sets and puts them in a neatly formatted matrix
Line B gets the first index of the max value from the column sums of the matrix in formed in line A.
The liklihood of outcomes {x_1...x_8} in 8 binomial experiments with 20 trials each with probability of success p is
$$ \prod_1^8{20\choose x_i}p^{x_i}(1-p)^{p-x_i} $$
The R code would be

<code>
prod(dbinom(x, prob = p, size = 20))
</code>
So the probability for the given values is 
```{r q2.2}
p=seq(0.01,1,by=.01)
plot(p,map(map(p,~dbinom(c(3,3,4,3,4,5,5,4),20,.x)),~max(.x)))
which.max(map(map(p,~dbinom(c(3,3,4,3,4,5,5,4),20,.x)),~max(.x)))
```
So the max likelihood is 15%

##Q3
The graphical solution yeilds 5.61
```{r t3}
f<-mymaxlik(
  x = c(4,6,7,6,5),
  param = seq(0, 20, length = 1000),
  lfun = logpoiss,
  xlab = expression(lambda),
  main = "Poisson",
  cex.main = 2
   
)
myNRML(
  x0 = 0.99,
  delta = 0.000001,
  llik = function(x){logpoiss(c(4,6,7,6,5),x)},
  xrange = c(0.01, 0.99),
  parameter = "p"
)
```



Algebraically, the likelihood is
$$ \prod{e^{-\lambda}}{\lambda^y\over y!} $$
which has max at 
$$ \hat{L} = \hat{\lambda = `r mean(4,6,7,6,5)`}$$

##Q4
```{r t4}
maxlikg2(c(2,6), c(4,10), lfun = logbin2())
```

