---
title: "Lab 11"
author: "Zane Gray"
date: "October 17, 2018"
output: 
  html_document:
    toc: yes
    toc_float: yes
    highlights: pygments
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(knitr)
library(kableExtra)
library(magrittr)
library(dplyr)
phishing=read.csv("../lab1/phishing.csv")
```
###7/16 questions completed
##Q1
The formula $\int{e^{-x/95}\over 95}dx = e^{-x/95}+c$ yeilds the probability of interarrival time x.
Using the definite integral yeilds a probability of `r 100*exp(-120/95)%>%round(.,digits=4)`%

```{r t1}
t.test(pexp(phishing$INTTIME,rate = 1/95),pexp(rexp(267)))
```
The confidence interval is very small compared to the varience, so the interarrival time is very likely to have an exponential sample distribution


##Q2 
for a gamma random variable, the mean and median are $\alpha\beta$ and $\alpha\beta^2$ respectively. Here, they are $\mu= `r 3*.07`$ and $\sigma^2 = `r 3*.07*.07`$  
The interval $\mu\pm 3*\sigma$ (the 95% confidence interval by Chebyshev's rule) is (`r 3*.07-3*sqrt(3*.07*.07)%>%round(.,4)`,`r 3*.07+3*sqrt(3*.07*.07)%>%round(.,4)`). This makes the all-time record flood level of .60 million cubic feet per second an extreme outlier.

##Q3
```{r t3}

df<-data.frame(
  A=c(4,8,pgamma(1,shape = 2,scale = 2)),
  B=c(4,16,pgamma(1,shape = 1, scale = 4)),
  names=c("mean","st dev","p(Y<1)"),
  row.names = "names")
df%>%
kable(col.names=c("Formula A","Formula B"))%>%
  kable_styling("striped","condensed")
```
Formula B has a higher probability after 1 minute.

##Q4
```{r t4}
pweibull(2,4,2)
qweibull(0.50,4,2)
```
$\sigma = `r (4^(1/2) *(gamma((2+2)/2)-(gamma((2+1)/2))^2))^0.5`$
$\mu\pm 2\sigma = (`r 1.77246-2*.9265`,`r 1.77246+2*.9265`)$  
The lower end of the interval is outside the support for a weibull, so the probability that Y is in the range is $P(Y\leq \mu+2\sigma)$ = `r dweibull(1.77246+2*.9265,4,2)`  
The likelihood of a washer needing its first repair after 6 years is `r pweibull(6,4,2,lower.tail=FALSE)`

##Q5
$\mu = `r 2/(2+9)`$  
$\sigma^2 = `r 2*9/((2+9)^2 * (2+9+1))`$  
`r 1-pbeta(0.40,2,9)`  
`r pbeta(.1,2,9)`

##Q6
$\alpha = 2, \beta = 16$  
$\mu = `r 4*(gamma(3/2))`$  
$\sigma^2 = `r 16*(gamma(2)-(gamma(3/2))^2)`$  
$\mu+x\sigma=6$ at $x = 1.333$

##Q7
$P(x,y)={1\over 6*6} = 1/36$  
$p_1(x)=p(x)=1/6$  
$p_2(y)=p(y)=1/6$  
$p_1(x|y)={1/36\over 1/6} = 1/6$  
$p_2(y|x)={1/36\over 1/6} = 1/6$  
Because $p(x)=p(x|y)$ and $p(y)=p(y|x)$ we can conclude that x and y are independant

##Q8
